\textbf{Discrete Bulk Reconstruction Problem} \\ \large Compiled Research

### 2025-03-31 paper.tex
Final Report

% Title Page
\title{\textbf{Discrete Bulk Reconstruction Problem} \\ \large Compiled Research}
\author{Piper Jeffries \\ Missouri S\&T \\ \texttt{pejbvy@umsystem.edu}}
\date{\today}

@@

%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    The \textbf{Discrete Bulk Reconstruction Problem (DBRP)} models the entanglement structure of quantum systems using discrete graphs. It is rooted in the Anti-de Sitter / Conformal Field Theory (AdS/CFT) correspondence, which connects a gravitational theory in AdS space (the bulk) to its quantum field theory on its boundary (the CFT).
    While this describes a universe different from our own, it offers valuable insights into quantum gravity and spacetime emergence. 
    \\
    \indent Instead of using traditional approaches that rely on continous AdS space, DBRP models the bulk as a graph, where nodes correspond to regions of space and edge weights encode entanglement connectivity.
    In this framework, geodesics in AdS are approximated by min-cuts in the graph, and the Ryu-Takayanagi (RT) formula determines minimal surfaces in the bulk, allowing for bulk geometry reconstruction from boundary entanglement.
    \\
   \indent DBRP leverages tensory networks and holography to provide a discrete approach to understanding spacetime, quantum entanglement, and information flow.
    DBRP could provide profound insight in quantum gravity, improved quantum error correction, and practical quantum computing applications.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{9}
    \bibitem{example}
    Scott Aaronson and Jason Pollack, \textit{Discrete bulk reconstruction}, 2023.
    \bibitem{2}
    Ronak Ramachandran, \textit{Further Exploration of the Discrete Bulk Reconstruction Problem}, 2023.
    \bibitem{AI}
    ChatGPT
\end{thebibliography}

>>>>

% Title Page
\title{\textbf{Discrete Bulk Reconstruction Problem} \\ \large Compiled Research}

\author{\small{Piper Jeffries, E-mail:} \texttt{pejbvy@umsystem.edu} \\ \small{Advisor: Dr. Avah Banerjee} \\ \small{Department of Computer Science, University of Missouri S\&T}}
\date{\small{\today}}

@@

%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    The \textbf{Discrete Bulk Reconstruction Problem (DBRP)} models the entanglement structure of quantum systems using discrete graphs. It is rooted in the Anti-de Sitter / Conformal Field Theory (AdS/CFT) correspondence, which connects a gravitational theory in AdS space to its quantum field theory on the CFT.
    While this describes a universe different from our own, it offers valuable insights into quantum gravity and spacetime emergence. 
    \\
    \indent DBRP models the bulk as a graph, where nodes correspond to regions of space and edge weights encode entanglement connectivity.
    In this framework, geodesics in AdS are approximated by min-cuts in the graph, and the Ryu-Takayanagi (RT) formula determines minimal surfaces in the bulk. DBRP leverages tensory networks and holography to provide a discrete approach to understanding spacetime, quantum entanglement, and information flow.
    DBRP could provide profound insight in quantum gravity, improved quantum error correction, and practical quantum computing applications.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%%%%%%
\section{References}
\renewcommand{\refname}{}
\begin{thebibliography}{9}
    \bibitem{example}
    Scott Aaronson and Jason Pollack, \textit{Discrete bulk reconstruction}, 2023.
    \bibitem{2}
    Ronak Ramachandran, \textit{Further Exploration of the Discrete Bulk Reconstruction Problem}, 2023.
    \bibitem{AI}
    ChatGPT
\end{thebibliography}
